Fourmile Calibrations

### 2023-02-21 calibration_output.Rmd
tmin and tmax monthly HRU vals

mar_tmax <- tm_shape(hrus_map_tmax_mar) +
  tm_polygons('mo_tmax_diff', id = 'value') +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=1) +
  tm_layout(title = 'March avg tmax')

@@

apr_tmax <- tm_shape(hrus_map_tmax_apr) +
  tm_polygons('mo_tmax_diff', id = 'value') +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=1) +
  tm_layout(title = 'April avg tmax')

@@

may_tmax <- tm_shape(hrus_map_tmax_may) +
  tm_polygons('mo_tmax_diff', id = 'value') +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=1) +
  tm_layout(title = 'May avg tmax')

@@

jun_tmax <- tm_shape(hrus_map_tmax_jun) +
  tm_polygons('mo_tmax_diff', id = 'value') +
tm_shape(locations_t) +
  tm_symbols(col='blue', size=1) +
  tm_layout(title = 'June avg tmax')

@@

## Cumulative Precip difference

@@

soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) +
  tm_polygons('avg_max_grid', midpoint = NA, id = 'value') +
  tm_legend(legend.outside = T) +
  tm_layout(title = 'Average max soil sat',
            title.position = c('left', 'top'))

>>>>

mar_tmax <- tm_shape(hrus_map_tmax_mar) +
  #tm_polygons('mo_tmax_diff', id = 'value') +
  tm_fill('mo_tmax_diff', id = 'value',
          breaks = c(-6,-3,0,3,6)) +
  tm_borders() +
  tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'March avg tmax',
            legend.outside = T)

@@

apr_tmax <- tm_shape(hrus_map_tmax_apr) +
  tm_fill('mo_tmax_diff', id = 'value',
          breaks = c(-6,-3,0,3,6)) +
  tm_borders() +
  tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'April avg tmax',
            legend.outside = T)

@@

may_tmax <- tm_shape(hrus_map_tmax_may) +
  tm_fill('mo_tmax_diff', id = 'value',
         breaks = c(-6,-3,0,3,6)) +
  tm_borders() +
tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'May avg tmax',
            legend.outside = T)

@@

jun_tmax <- tm_shape(hrus_map_tmax_jun) +
  tm_fill('mo_tmax_diff', id = 'value',
          breaks = c(-6,-3,0,3,6)) +
  tm_borders() +
tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'June avg tmax',
            legend.outside = T)

@@

## Tmin monthly average

```{r tmin month, echo = F}
tmin_grid_mo <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tminAll_prism.csv') %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmin_grid') %>%
  mutate(time = dmy(time),
         month = month(time)) %>%
  filter(month %in% c(3:6)) %>%
  group_by(value, month) %>%
  summarize(avg_tmin_grid = mean(tmin_grid))

tmin_statn_mo <- read_csv('C:/Users/sears/Documents/Repos/fourmile/HRU_output/reg_tminAll.csv') %>% 
  pivot_longer(cols = `3`:`19`,
               names_to = 'value', 
               values_to = 'tmin_statn') %>%
  mutate(time = dmy(time),
         month = month(time)) %>%
  filter(month %in% c(3:6)) %>%
  group_by(value, month) %>%
  summarize(avg_tmin_statn = mean(tmin_statn))

tmin_hrus_mo <- left_join(tmin_grid_mo, tmin_statn_mo, by = c('value', 'month')) %>%
  mutate(mo_tmin_diff = avg_tmin_statn - avg_tmin_grid,
         value = as.numeric(value))

#march
tmin_hrus_mar<- tmin_hrus_mo %>%
  filter(month == 3)

hrus_map_tmin_mar <- left_join(hrus, tmin_hrus_mar, by = 'value')

mar_tmin <- tm_shape(hrus_map_tmin_mar) +
  #tm_polygons('mo_tmin_diff', id = 'value') +
  tm_fill('mo_tmin_diff', id = 'value',
          breaks = c(-5,-2.5,0,2.5,5)) +
  tm_borders() +
  tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'March avg tmin',
            legend.outside = T)

#april
tmin_hrus_apr<- tmin_hrus_mo %>%
  filter(month == 4)

hrus_map_tmin_apr <- left_join(hrus, tmin_hrus_apr, by = 'value')

apr_tmin <- tm_shape(hrus_map_tmin_apr) +
  tm_fill('mo_tmin_diff', id = 'value',
          breaks = c(-5,-2.5,0,2.5,5)) +
  tm_borders() +
  tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'April avg tmin',
            legend.outside = T)

#may
tmin_hrus_may<- tmin_hrus_mo %>%
  filter(month == 5)

hrus_map_tmin_may <- left_join(hrus, tmin_hrus_may, by = 'value')

may_tmin <- tm_shape(hrus_map_tmin_may) +
  tm_fill('mo_tmin_diff', id = 'value',
         breaks = c(-5,-2.5,0,2.5,5)) +
  tm_borders() +
tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'May avg tmin',
            legend.outside = T)

#june
tmin_hrus_jun<- tmin_hrus_mo %>%
  filter(month == 6)

hrus_map_tmin_jun <- left_join(hrus, tmin_hrus_jun, by = 'value')

jun_tmin <- tm_shape(hrus_map_tmin_jun) +
  tm_fill('mo_tmin_diff', id = 'value',
          breaks = c(-5,-2.5,0,2.5,5)) +
  tm_borders() +
tm_shape(locations_t) +
  tm_symbols(col='blue', size = 0.25) +
  tm_layout(title = 'June avg tmin',
            legend.outside = T)

tmap_arrange(mar_tmin, apr_tmin, may_tmin, jun_tmin)

```{r tmax month, echo = F}
## Cumulative Precip difference

@@

soilavg_grid_max <- tm_shape(hrus_map_soilsat_max) +
  tm_polygons('avg_max_grid', midpoint = NA, id = 'value') +
  tm_legend(legend.outside = T) +
  tm_layout(main.title = 'Average max soil sat',
            title.position = c('left', 'top'))
